term paper_TTTTTest

### 2024-02-13 outputs/paper/paper.qmd
testtt

---
title: "term papaer 2"
author: "Hao Wang  Siqi Fei Xuecheng Gao"
thanks: "Code and data are available at: https://github.com/groundUofT888/Term-Paper-2.git ; Replication on Social Science Reproduction platform available at: www.aeaweb.org/articles?id=10.1257/app.20210529"
date: "February 12, 2024"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: " "
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes 
nocite: '@*'
bibliography: references.bib
---

>>>>

---
title: "term paper_TTTTTest"
author: "Hao Wang  Siqi Fei Xuecheng Gao"
thanks: "Code and data are available at: https://github.com/groundUofT888/Term-Paper-2.git ; Replication on Social Science Reproduction platform available at: www.aeaweb.org/articles?id=10.1257/app.20210529"
date: "February 12, 2024"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: " "
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes 
nocite: '@*'
bibliography: references.bib
---
